Waving and swaying

### 2014-04-10 Paper/grass.tex
"add new graphs"

The variation of critical wave number with shear layer thickness for different grass height is shown in Figure \ref{K_vs_shear}. This variation of critical 
wavenumber with shear layer thickness can be divided into three distinct region. First, the region where critical wavelength does not increases linearly with the
increase of the shear layer thickness, this region occur for canopies with thick shear layer $H/\delta <10$. Second region identified as shear layer region, where variation in critical
wavelength is proportional to the variation in shear layer thickness, the instability in this region can be understood to arise from a mechanism similar to Kelin-Helmholtz instability 
observed in the free shear flow. Third, the region where critical wavelength does not vary with the variation of shear layer thickness. The boundary of these region depends on 
submergence ratio and the shear layer thickness experienced by the canopy.

>>>>

The variation of critical wave number with the variation in $\delta$ for different grass height is shown in Figure \ref{K_vs_shear}, where we can observe that above a 
certain threshold $\delta$ the critical wavelength decreases with the decrease in $\delta$, similar to the one predicted by K-H theory based on the instability of free shear flow, for that
reason this region is identified as shear layer region. We also observe that once the $\delta$ is decreased below the threshold value, there isn't any variation in the 
critical wavelength with the decrease of shear layer thickness and $\lambda_{critical} \sim (H-h_{grass})$, we identify this region as shear instability of unvegetated region.
The boundary of transition from instability of shear-layer near the tip of grass to the instability of unvegetated flow depends on the submergence ratio of grass. 
%    This variation of critical 
%wavenumber with shear layer thickness can be divided into three distinct region. First, the region where critical wavelength does not increases linearly with the
%increase of the shear layer thickness, this region occur for canopies with thick shear layer $H/\delta <10$. Second region identified as shear layer region, where variation in critical
%wavelength is proportional to the variation in shear layer thickness, the instability in this region can be understood to arise from a mechanism similar to Kelin-Helmholtz instability 
%observed in the free shear flow. Third, the region where critical wavelength does not vary with the variation of shear layer thickness. The boundary of these region depends on 
%submergence ratio and the shear layer thickness experienced by the canopy.
